An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-08 jmiv.tex
relec HT

\author{Daniel Antunes%\inst{1}
\and Jacques-Olivier Lachaud%\inst{1}
\and Hugues Talbot%\inst{2}
}
%
\authorrunning{D. Antunes et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{%Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
  Daniel Antunes \at
  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
  \email{daniel.martins-antunes@univ-smb.fr} \and
  Jacques-Olivier~Lachaud \at  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
  \email{jacques-olivier.lachaud@univ-smb.fr} \and
  Hugues Talbot \at CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
  \email{hugues.talbot@centralesupelec.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
    Mumford-Shah functional uses region perimeter as prior. This has inspired much research in the last few decades,
    with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
    binary perimeter prior. It has been observed that this prior is not suitable in many applications, for example for
    segmenting thin objects or some textures, which may have high perimeter/surface ratio. Mumford observed that an
    interesting prior for natural objects is the Euler Elastical model, which involves the squared curvature. In other
    areas of science, researchers have noticed that some physical binarization processes, like emulsion unmixing can be
    well-approximated by curvature-related flow like the Willmore flow. 
    However, curvature-related flows are not easy to compute because curvature is difficult to estimate accurately, and the
    underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
    approximates an Elastica-related flow using a multigrid-convergent curvature estimator, within a discrete
    variational framework. We also present an application of this model as a post-processing step to a segmentation
    framework.
\keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction} %% \todo{(To be extended)}}

@@

\section{Multigrid convergent estimators}

The goal of this section is to  introduce the concept of multigrid convergenc and its potential when analyzing digital images with variational models involving geometric quantities. More precisely we wish to delineate shapes within digital images with some priors related to their unknown continuous geometry. Of course we only observe shape digitizations within images.

>>>>

\author{Daniel Antunes%\inst{1}
\and Jacques-Olivier Lachaud%\inst{1}
\and Hugues Talbot%\inst{2}
}
%
\authorrunning{D. Antunes et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{%Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
  Daniel Antunes \at
  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
  \email{daniel.martins-antunes@univ-smb.fr} \and
  Jacques-Olivier~Lachaud \at  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
  \email{jacques-olivier.lachaud@univ-smb.fr} \and
  Hugues Talbot \at CentraleSupelec, Inria, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
  \email{hugues.talbot@centralesupelec.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
    Mumford-Shah functional uses region perimeter as prior. This has inspired much research in the last few decades,
    with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
    binary perimeter prior. It has been observed that this prior is not suitable in many applications, for example for
    segmenting thin objects or some textures, which may have high perimeter/surface ratio. Mumford observed that an
    interesting prior for natural objects is the Euler Elastical model, which involves the squared curvature. In other
    areas of science, researchers have noticed that some physical binarization processes, like emulsion unmixing can be
    well-approximated by curvature-related flow like the Willmore flow. 
    However, curvature-related flows are not easy to compute because curvature is difficult to estimate accurately, and the
    underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
    approximates an Elastica-related flow using a multigrid-convergent curvature estimator, within a discrete
    variational framework. We also present an application of this model as a post-processing step to a segmentation
    framework.
\keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction} %% \todo{(To be extended)}}

@@

\section{Multigrid convergent estimators}
Our objective is to delineate shapes within digital images with some priors related to continuous geometry. The goal of
this section is to introduce the concept of multigrid convergence and its potential when analyzing digital images with
variational models involving geometric quantities, with the constraint that only digitized shapes are observed.
